Transfer Learning in Visual and Relational Reasoning

### 2020-02-13 Transfer_Learning/arxiv_version/arxiv_paper_main.tex
Submitted files to arxiv in a single folder
Margin
Arxiv version 2 initial commit
Fixed author affiliations and added new abstract

@@

\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{times}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amsmath, amssymb, amsfonts,bm}
\usepackage{amsthm}

@@

\usepackage{cleveref}
\crefname{section}{Section}{Sections}
\crefname{figure}{Figure}{Figures}
\crefname{table}{Table}{Tables}
\crefname{appendix}{Appendix}{Appendices}
\crefname{definition}{Definition}{Definitions}

@@

%%%%%%%%% AUTHORS
% WILL NEED TO REARRANGE THE AUTHORS LIST & GET CORRECT INSTITUTIONS / EMAILS
\author{%
T.S. Jayram\thanks{\textit{Almaden Research Center, San Jose, CA, USA}.} \hspace{1cm} \and  
Vincent Marois\thanks{\textit{Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \hspace{1cm} \and 
Tomasz Kornuta\thanks{Currently at Nvidia. \textit{Santa Clara, CA, USA}.} \and
\hspace{2cm} Vincent Albouy\footnotemark[1]  \hspace{1cm} \and 
Emre Sevgen\thanks{Currently at Citrine Informatics}  \hspace{1cm} \and 
Ahmet S. Ozcan\footnotemark[1] \and \\
IBM Research AI
}

@@

\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
  Transfer learning is becoming the de facto solution for vision and text encoders in the front-end processing of machine learning solutions. Utilizing vast amounts of knowledge in pre-trained models and subsequent fine-tuning allows achieving better performance in domains where labeled data is limited. In this paper, we analyze the efficiency of transfer learning in visual reasoning by introducing a new model (SAMNet) and testing it on two datasets: COG and CLEVR.  Our new model achieves state-of-the-art accuracy on COG and shows significantly better generalization capabilities compared to the baseline. We also formalize a taxonomy of transfer learning for visual reasoning around three axes: feature, temporal, and reasoning transfer. Based on extensive experimentation of transfer learning on each of the two datasets, we show the performance of the new model along each axis.
\end{abstract}

%%%%%%%%% BODY TEXT
\input{introduction}

>>>>

\RequirePackage{snapshot}

@@

\usepackage[letterpaper,margin=1in]{geometry}
\usepackage[auth-sc,affil-sl]{authblk}
\usepackage{times}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amsmath, amssymb, amsfonts,bm}
\usepackage{amsthm}

@@

\usepackage[hyperpageref]{backref}
\usepackage{cleveref}
\crefname{section}{Section}{Sections}
\crefname{figure}{Figure}{Figures}
\crefname{table}{Table}{Tables}
\crefname{appendix}{Appendix}{Appendices}
\crefname{definition}{Definition}{Definitions}

@@

%%%%%%%%% AUTHORS
% WILL NEED TO REARRANGE THE AUTHORS LIST & GET CORRECT INSTITUTIONS / EMAILS
%\author{%
%T.S. Jayram\thanks{\textit{IBM Almaden Research Center, San Jose, CA, USA}.} \hspace{1.5cm} \and  
%Vincent Marois\thanks{\textit{IBM Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \hspace{1.5cm} \and 
%Tomasz Kornuta\thanks{Currently at NVIDIA. \textit{Santa Clara, CA, USA}.}  \and
%\hspace{1cm} Vincent Albouy\footnotemark[1]  \hspace{1.5cm} \and 
%Emre Sevgen\thanks{Currently at Citrine Informatics.}  \hspace{1.5cm} \and 
%Ahmet S. Ozcan\footnotemark[1] \and \\
%{\large IBM Research AI}
%}

\newcommand\blfootnote[1]{%
	\begingroup
	\renewcommand\thefootnote{}\footnote{#1}%
	\addtocounter{footnote}{-1}%
	\endgroup
}

\renewcommand\Authands{ and }
\author[1]{T.S. Jayram}
\author[2]{Vincent Marois}
\author[3]{Tomasz Kornuta}
\author[ ]{Vincent Albouy\thanks{Work done while at IBM Research AI, Almaden Research Center}}
\author[*]{\\Emre Sevgen}
\author[1]{Ahmet Ozcan}
\affil[1]{IBM Research AI, Almaden Research Center, San Jose, CA, USA.}
\affil[2]{IBM Research AI, Thomas J. Watson Research Center, Yorktown, NY, USA.}
\affil[3]{NVIDIA, Santa Clara, CA, USA}

@@

\maketitle
\blfootnote{E-mail: {\scriptsize \textit{\{jayram,asozcan\}@us.ibm.com,  \{vincent.marois,vincent.albouy\}@ibm.com, tkornuta@nvidia.com, sesevgen@gmail.com}}}

%%%%%%%%% ABSTRACT
\begin{abstract}
	Transfer learning has become the de facto standard in computer vision and natural language processing, especially where labeled data is scarce. Accuracy can be significantly improved by using pre-trained models and subsequent fine-tuning. In visual reasoning tasks, such as image question answering, transfer learning is more complex. In addition to transferring the capability to recognize visual features, we also expect to transfer the system’s ability to reason. Moreover, for video data, temporal reasoning adds another dimension. In this work, we formalize these unique aspects of transfer learning and propose a theoretical framework for visual reasoning, exemplified by the well-established CLEVR and COG datasets. Furthermore, we introduce a new, end-to-end differentiable recurrent model (SAMNet), which shows state-of-the-art accuracy and better performance in transfer learning on both datasets. The improved performance of SAMNet stems from its capability to decouple the abstract multi-step reasoning from the length of the sequence and its selective attention enabling to store only the question-relevant objects in the external memory.
\end{abstract}

%%%%%%%%% BODY TEXT
%%%%%%%%% BODY TEXT
\input{introduction}
